Meta RL analyses

### 2019-01-22 meta_RL_analyses.Rmd
Language analyses

result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho")

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic_only_one_ho", "nometa_only_one_ho")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho"), num_runs, "new_meta_true_losses")

>>>>

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
                   "language")

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

# language results

```{r}
language_d = load_d(results_dir, result_subdirs, num_runs, "new_language_rewards")

language_d = language_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
```

```{r}
avg_language_d = language_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(run_type, game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
                               "language"), num_runs, "new_meta_true_losses")
